Manuscript

### 2018-11-06 manuscript.Rmd

  plot_p_point <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    scale_y_continuous(breaks = pretty_breaks()) +
    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
    geom_text(data = g2p_druggenelin_all_summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
    labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

  plot_p_box <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(ylim = c(0, 1)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
    coord_flip() +
    labs(x = "Level A G2P\nassociation") +
    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

  plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage_name, margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

  saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_by_lineage/", lineage_name, "_g2p_evidence_plotly.html"))
}
```

@@

```{r}
ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q3_g2pgenes.rds")
ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)

ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q3_g2pgenes.rds")
ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)

gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q3_g2pgenes.rds")
gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)

@@

# Gene expression

@@

@@

```{r fig.height=4, fig.width=8}
g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally()
g2p_druggene_p_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, ctrp_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE, suffixes = c("_CCLE", "_CTRP"))
g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, gdsc_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CCLE"] <- "CCLE"
colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CTRP"] <- "CTRP"
colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p"] <- "GDSC"
g2p_druggene_p_summ_melt <- melt(g2p_druggene_p_summ, id.vars = c("Drug_Gene", "n"), measure.vars = c("CCLE", "CTRP", "GDSC"), variable.name = "Dataset", value.name = "p")

@@

plot_mad_box <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_violin(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.75, width = 0.25) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

@@

g2p_druggene_all_mad_summ_plot <- cowplot::plot_grid(plot_mad_box,
                   plot_mad_point,
                   nrow = 2,
                   rel_heights = c(1, 4))
g2p_druggene_all_mad_summ_plot
# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_mad_summ_plot.png", g2p_druggene_all_mad_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")

@@

g2p_druggene_all_p_summ_plot <- cowplot::plot_grid(plot_p_box,
                   plot_p_point,
                   nrow = 2,
                   rel_heights = c(1, 4))
g2p_druggene_all_p_summ_plot
# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.png", g2p_druggene_all_p_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

```{r}
plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

@@

```{r}
g2p_druggenelin_p_tally <- g2p %>% group_by(Drug_Gene, group_general_lineage_name) %>% tally()

ccle_druggenelin_p_summ <- ccle_signif_g2p_lineage
ccle_druggenelin_p_summ$Drug_Gene <- paste0(ccle_druggenelin_p_summ$Drug, "_", ccle_druggenelin_p_summ$Hugo_Symbol)
ccle_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ccle_druggenelin_p_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
ccle_druggenelin_summ$n <- ifelse(is.na(ccle_druggenelin_summ$n), 0, ccle_druggenelin_summ$n)
ccle_druggenelin_summ$InG2P <- ifelse(ccle_druggenelin_summ$n != 0, "Yes", "No")
ccle_druggenelin_summ$Dataset <- "CCLE"

@@

@@

## Figure 1

>>>>

  plot_point <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    scale_y_continuous(breaks = pretty_breaks()) +
    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
    geom_text(data = g2p_druggenelin_all_summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
    labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

  plot_box <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(ylim = c(0, 1)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.5) +
    coord_flip() +
    labs(x = "Level A G2P\nassociation") +
    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage_name, margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

  saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_p_by_lineage/", lineage_name, "_g2p_evidence_p_plotly.html"))
}
```

@@

```{r}
ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q3_g2pgenes.rds")
ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
ccle_data_ptmuts$Dataset <- "CCLE"

ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q3_g2pgenes.rds")
ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
ctrp_data_ptmuts$Dataset <- "CTRP"

gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q3_g2pgenes.rds")
gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
gdsc_data_ptmuts$Dataset <- "GDSC"

@@

@@

```{r}
g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally()
```

@@

```{r fig.height=4, fig.width=8}
g2p_druggene_p_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, ctrp_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE, suffixes = c("_CCLE", "_CTRP"))
g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, gdsc_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CCLE"] <- "CCLE"
colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CTRP"] <- "CTRP"
colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p"] <- "GDSC"
g2p_druggene_p_summ_melt <- melt(g2p_druggene_p_summ, id.vars = c("Drug_Gene", "n"), measure.vars = c("CCLE", "CTRP", "GDSC"), variable.name = "Dataset", value.name = "p")

@@

plot_mad_box <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_violin(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.75, width = 0.5) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

@@

g2p_druggene_all_mad_summ_plot <- cowplot::plot_grid(plot_mad_box,
                   plot_mad_point,
                   nrow = 2,
                   rel_heights = c(1.5, 4))
g2p_druggene_all_mad_summ_plot
# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_mad_summ_plot.png", g2p_druggene_all_mad_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")

@@

g2p_druggene_all_p_summ_plot <- cowplot::plot_grid(plot_p_box,
                   plot_p_point,
                   nrow = 2,
                   rel_heights = c(1.5, 4))
g2p_druggene_all_p_summ_plot
# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.png", g2p_druggene_all_p_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

```{r, eval=FALSE}
plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

@@

```{r}
ccle_druggenelin_p_summ <- ccle_signif_g2p_lineage
ccle_druggenelin_p_summ$Drug_Gene <- paste0(ccle_druggenelin_p_summ$Drug, "_", ccle_druggenelin_p_summ$Hugo_Symbol)
ccle_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ccle_druggenelin_p_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
ccle_druggenelin_summ$n <- ifelse(is.na(ccle_druggenelin_summ$n), 0, ccle_druggenelin_summ$n)
ccle_druggenelin_summ$InG2P <- ifelse(ccle_druggenelin_summ$n != 0, "Yes", "No")
ccle_druggenelin_summ$Dataset <- "CCLE"

@@

### Gene expression

```{r}
drugscreen_ptmuts <- rbind(ccle_data_ptmuts, ctrp_data_ptmuts, gdsc_data_ptmuts)
```

```{r}
summ <- ccle_data_ptmuts %>% count(group_general_lineage_name, Drug_Gene)
```

```{r}
PearsonByLineage <- function(lineage, dataset) {
  use_data <- filter(dataset, group_general_lineage_name == lineage)
  if(nrow(use_data) == 0) {
    use_data <- NA
  }
  # use_data_summ <- use_data %>% count(Drug_Gene)
  # use_data_summ <- filter(use_data_summ, n >= 3)
  # use_data <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
  # 
  # pearson_res <- use_data %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
  # pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
  # pearson_res$group_general_lineage_name <- lineage

  return(use_data)
}

# test <- PearsonByLineage("breast cancer", ccle_data_ptmuts)

# ccle_signif_pearson <- lapply(as.character(unique(ccle_data_ptmuts$group_general_lineage_name)), PearsonByLineage, dataset = ccle_data_ptmuts)
```

```{r}
PearsonPlotlyByLineage <- function(lineage) {

  ticker <- 0

  use_data_ccle <- filter(use_data, Dataset == "CCLE")
  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
  if(nrow(use_data_ccle_summ) <= 1) {
    ccle_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_ttest_res <-  NA }
  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
    ccle_ttest_res <- paste0("t = ", round(ccle_lin_p_ttest$statistic, 3), ", df = ", round(ccle_lin_p_ttest$parameter, 3), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
  }

  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
  if(nrow(use_data_ctrp_summ) <= 1) {
    ctrp_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_ttest_res <-  NA }
  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
    ctrp_ttest_res <- paste0("t = ", round(ctrp_lin_p_ttest$statistic, 3), ", df = ", round(ctrp_lin_p_ttest$parameter, 3), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
  }

  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
  if(nrow(use_data_gdsc_summ) <= 1) {
    gdsc_ttest_res <-  NA
    ticker <- t                                                                                                                                                                                                                icker + 1
    }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_ttest_res <-  NA }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
    gdsc_ttest_res <- paste0("t = ", round(gdsc_lin_p_ttest$statistic, 3), ", df = ", round(gdsc_lin_p_ttest$parameter, 3), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
  }

  g2p_druggenelin_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_ttest_res, ctrp_ttest_res, gdsc_ttest_res))
  # use_data_summ <- use_data %>% count(InG2P)
  # if(nrow(use_data_ccle_summ) <= 1) { ttest_res <- NA }
  # else if(use_data_summ[use_data_summ$InG2P == "Yes",]$nn < 2) { ttest_res <- NA }
  # else if(use_data_summ[use_data_summ$InG2P == "Yes",]$nn >= 2) {
  #   ttest <- t.test(use_data$p ~ use_data$InG2P)
  #   ttest_res <- paste0("t = ", round(ttest$statistic, 3), ", df = ", round(ttest$parameter, 3), ", p = ", round(ttest$p.value, 3))
  # }
}
```

```{r}
ccle_pearson_res <- ccle_data_ptmuts %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
ccle_pearson_res <- merge(g2p_druggene_p_tally, ccle_pearson_res, by = "Drug_Gene", all.y = TRUE)
ccle_pearson_res$n <- ifelse(is.na(ccle_pearson_res$n), 0, ccle_pearson_res$n)
ccle_pearson_res$InG2P <- ifelse(ccle_pearson_res$n != 0, "Yes", "No")
ccle_pearson_res$Dataset <- "CCLE"
ccle_pearson_ttest <- t.test(ccle_pearson_res$Pearson_Corr ~ ccle_pearson_res$InG2P)
ccle_pearson_ttest_res <- paste0("t = ", round(ccle_pearson_ttest$statistic, 3), ", df = ", round(ccle_pearson_ttest$parameter, 3), ", p = ", round(ccle_pearson_ttest$p.value, 3))

ctrp_pearson_res <- ctrp_data_ptmuts %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
ctrp_pearson_res <- merge(g2p_druggene_p_tally, ctrp_pearson_res, by = "Drug_Gene", all.y = TRUE)
ctrp_pearson_res$n <- ifelse(is.na(ctrp_pearson_res$n), 0, ctrp_pearson_res$n)
ctrp_pearson_res$InG2P <- ifelse(ctrp_pearson_res$n != 0, "Yes", "No")
ctrp_pearson_res$Dataset <- "CTRP"
ctrp_pearson_ttest <- t.test(ctrp_pearson_res$Pearson_Corr ~ ctrp_pearson_res$InG2P)
ctrp_pearson_ttest_res <- paste0("t = ", round(ctrp_pearson_ttest$statistic, 3), ", df = ", round(ctrp_pearson_ttest$parameter, 3), ", p = ", round(ctrp_pearson_ttest$p.value, 3))

gdsc_pearson_res <- gdsc_data_ptmuts %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
gdsc_pearson_res <- merge(g2p_druggene_p_tally, gdsc_pearson_res, by = "Drug_Gene", all.y = TRUE)
gdsc_pearson_res$n <- ifelse(is.na(gdsc_pearson_res$n), 0, gdsc_pearson_res$n)
gdsc_pearson_res$InG2P <- ifelse(gdsc_pearson_res$n != 0, "Yes", "No")
gdsc_pearson_res$Dataset <- "GDSC"
gdsc_pearson_ttest <- t.test(gdsc_pearson_res$Pearson_Corr ~ gdsc_pearson_res$InG2P)
gdsc_pearson_ttest_res <- paste0("t = ", round(gdsc_pearson_ttest$statistic, 3), ", df = ", round(gdsc_pearson_ttest$parameter, 3), ", p = ", round(gdsc_pearson_ttest$p.value, 3))

g2p_druggene_pearson <- rbind(ccle_pearson_res, ctrp_pearson_res, gdsc_pearson_res)
g2p_druggene_pearson_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_PearCorr = c(ccle_pearson_ttest_res, ctrp_pearson_ttest_res, gdsc_pearson_ttest_res))
```

```{r fig.height=5, fig.width=12}
plot_pearson_point <- ggplot(data = g2p_druggene_pearson) +
  facet_wrap(~ Dataset) +
  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = Pearson_Corr, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = -0.05, y = 110, label = Test_Results_PearCorr)) +
  labs(x = "Pearson correlation coefficient between gene-drug AUC and gene expression", y = "Number of level A G2P associations") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_pearson_box <- ggplot(data = g2p_druggene_pearson) +
  facet_wrap(~ Dataset) +
  geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.75, width = 0.25) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

plot_pearson_point <- ggplot_gtable(ggplot_build(plot_pearson_point))
plot_pearson_box <- ggplot_gtable(ggplot_build(plot_pearson_box))
p_maxWidth <-  grid::unit.pmax(plot_pearson_point$widths, plot_pearson_box$widths)
plot_pearson_point$widths <- as.list(p_maxWidth)
plot_pearson_box$widths <- as.list(p_maxWidth)

g2p_druggene_pearson_plot <- cowplot::plot_grid(plot_pearson_box, plot_pearson_point, nrow = 2, rel_heights = c(1.5, 4))
g2p_druggene_pearson_plot
# ggsave("./plots_18Q3/manuscript/g2p_druggene_pearson_plot.png", g2p_druggene_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

```{r, eval=FALSE}
plot_pearson_point <- ggplot(data = g2p_druggene_pearson) +
  facet_wrap(~ Dataset) +
  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = Pearson_Corr, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = -0.05, y = 110, label = Test_Results_PearCorr)) +
  labs(x = "Pearson correlation coefficient between gene-drug AUC and gene expression", y = "Number of level A G2P associations") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_pearson_box <- ggplot(data = g2p_druggene_pearson) +
  facet_wrap(~ Dataset) +
  geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.75, width = 0.25) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

plot <- subplot(plot_pearson_box, plot_pearson_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between gene-drug AUC and gene expression"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_pearson_plot.html")
```

@@

## G2P genes
